---
title: "Analysis for the Stress and Honesty project"
author: "Ana Martinovici"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_float: 
            collapsed: false
        number_sections: true
        code_folding: hide
        theme: cerulean
editor_options: 
  chunk_output_type: console
---

This file includes the analysis for "The effect of acute stress on dishonesty: the moderating role of moral default" (Sebastian P.H. Speer, Ana Martinovici, Ale Smidts, Maarten A.S. Boksem).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library("tidyverse")
library("rstan")
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())	
choice_model <- stan_model(here::here("LOGIT.stan"))
```


```{r }
load(here::here("data.RData"))
source(here::here("f_aux_functions.R"))
choice_pars <- c("gamma_00", "gamma_std_cheat", "gamma_stress", "gamma_std_cheat_stress")

n_chains <- 10
n_iter   <- 10000

```

# Data summaries

We have `r nrow(part_info)` participants. 

Gender split: `r knitr::kable(part_info %>% group_by(Gender) %>% summarise(n = n()))` 

Age (values rounded to 2 decimals): 
mean = `r round(mean(part_info[["Age"]]), 2)` and 
SD = `r round(sd(part_info[["Age"]]), 2)`.

Each participant completes the same number of tasks, see that the min and max number of tasks per participant are equal:

```{r data-part1}
knitr::kable(part_and_task_info %>%
		 	group_by(participant_ID) %>%
		 	summarise(n_tasks_per_i = n()) %>%
		 	summarise(min_n_tasks = min(n_tasks_per_i),
		 		    max_n_tasks = max(n_tasks_per_i)))
```

Not all tasks provide an opportunity to cheat. For some tasks, participants had to use a mouse to indicate the differences between pictures, so there was no opportunity to say "Yes, I found all 3 differences" without showing them. 
All participants complete the same number of **click tasks**, see that the min and max number of click tasks are equal:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "click") %>%
		 	group_by(participant_ID) %>%
		 	summarise(n_tasks_per_i = n()) %>%
		 	summarise(min_n_tasks = min(n_tasks_per_i),
		 		    max_n_tasks = max(n_tasks_per_i)))

```

For click trials, each participant had exactly 6 normal trials (reward of 5 cents), 3 hard trials (reward of 20 cents), and 3 very hard trials (reward of 40 cents):

```{r}

knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "click") %>%
		 	group_by(participant_ID,
		 		   reward) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	group_by(reward) %>%
		 	summarise(min_n_tasks = min(n_tasks),
		 		    max_n_tasks = max(n_tasks)))


```

For no-click tasks, the split between trials with 1, 2, or 3 differences is:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "noclick") %>% 
		 	group_by(n_differences) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	mutate(perc_tasks = n_tasks / sum(n_tasks)),
		 digits = 2)

```

For no-click tasks, the split by reward:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "noclick") %>% 
		 	group_by(reward) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	mutate(perc_tasks = n_tasks / sum(n_tasks)),
		 digits = 2)

```

For no-click trials with three differences, the split by reward is:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "noclick") %>% 
		 	filter(n_differences == 3) %>%
		 	group_by(reward) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	mutate(perc_tasks = n_tasks / sum(n_tasks)),
		 digits = 2)

```

For trials with 1 or 2 differences, the split between normal and hard or very hard is:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "noclick") %>% 
		 	filter(n_differences %in% c(1, 2)) %>%
		 	mutate(difficulty = if_else(reward %in% c(0.20, 0.40), "hard or very hard", "normal")) %>%
		 	group_by(difficulty) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	mutate(perc_tasks = n_tasks / sum(n_tasks)),
		 digits = 2)

```



# Results

## Plot % cheating in first half

```{r}

df_plot <- part_and_task_info %>%
	filter(type_of_task == "noclick") %>%
	filter(n_differences %in% c(1, 2)) %>%
	filter(reward %in% c(0.20, 0.40)) %>%
	filter(part_response %in% c("No, did not find 3 diffs", "Yes, found 3 diffs")) %>%
	filter(is_in_second_half == 0)

df_plot <- df_plot %>%
	group_by(participant_ID) %>%
	summarise(n_tasks = n(),
		    n_cheated = sum(part_response == "Yes, found 3 diffs"),
		    perc_cheating = n_cheated / n_tasks) %>%
	ungroup()

mean_cheating <- mean(df_plot$perc_cheating)
sd_cheating   <- sd(df_plot$perc_cheating)

df_plot <- df_plot %>%
	mutate(std_perc_cheating = (perc_cheating - mean_cheating) / sd_cheating)

bottom_10perc <- quantile(df_plot$std_perc_cheating, probs = c(0.10))
top_10perc    <- quantile(df_plot$std_perc_cheating, probs = c(0.90))

df_plot <- df_plot %>%
	mutate(is_between_bottom_top_10perc = 
		 	(std_perc_cheating >= bottom_10perc)*
		 	(std_perc_cheating <= top_10perc))

df_plot <- df_plot %>%
	arrange(perc_cheating) %>%
	mutate(cheat_number = row_number()) %>%
	mutate(f_fill = factor(is_between_bottom_top_10perc,
				     levels = c(0, 1),
				     labels = c("bottom", "middle")))

figure2 <- df_plot %>% 
	ggplot(aes(x = cheat_number, y = perc_cheating)) +
	geom_col(aes(fill = f_fill), width = 0.9) +
	theme_bw() +
	ylab("Percent cheating at t = 1") +
	xlab("Participant") +
	scale_x_continuous(breaks = c(1, 60, 120)) + 
	scale_fill_manual("", 
				breaks = c("bottom", "middle"),
				values = c("middle" = "lightblue",
					     "bottom" = "grey75"),
				labels = c("bottom" = "Bottom 10% and top 10%",
					     "middle" = paste0("Analysis sample (n = ", 
					     			nrow(df_plot %>%
					     			     	filter(is_between_bottom_top_10perc == 1)),
					     			")"))) +
	guides(fill = guide_legend(nrow = 2)) +
	theme(legend.position = "bottom") 

figure2

```


```{r, echo = FALSE, include = FALSE}

setEPS()
postscript(here::here("figure2.eps"))
figure2
dev.off()

png(filename = here::here("figure2.png"), 
    width = 15, height = 10, units = "cm", res = 300)
figure2
dev.off()

```

The average percent cheating for the bottom 10% and top 10% is:

```{r}

knitr::kable(df_plot %>%
		 	filter(is_between_bottom_top_10perc == 0) %>%
		 	mutate(group_name = if_else(std_perc_cheating < 0, "bottom_10", "top_10")) %>%
		 	group_by(group_name) %>%
		 	summarise(n_obs = n(),
		 		    mean_perc_cheating = mean(perc_cheating),
		 		    mean_cheated = round(mean(n_cheated), 0),
		 		    mean_tasks = round(mean(n_tasks), 0)),
		 digits = 2)


```


## Model estimation results

Exclude participants in the tom 10% and bottom 10%, based on cheating percentile.

```{r WO_top10_bottom10}
WO_top10_bottom10_df <- f_prep_use_tasks(part_info = part_info, 
						     part_and_task_info = part_and_task_info,
						     exclusion_C1 = "no_exclusion", 
						     exclusion_C2 = "top_bottom_10")
WO_top10_bottom10_stan_data <- f_prep_stan_data(use_tasks = WO_top10_bottom10_df[["use_tasks"]])

WO_top10_bottom10_choice_fit <- sampling(choice_model, 
						     data = WO_top10_bottom10_stan_data,
						     chains = n_chains, 
						     iter = n_iter, 
						     seed = 25,
						     save_warmup = FALSE)
```

Check convergence (Rhat values should be 1):

```{r}

summary(summary(WO_top10_bottom10_choice_fit)[["summary"]][, "Rhat"])

```

Estimation results are:

```{r}
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_top10_bottom10_choice_fit), 
		 digits = c(0, 2, 2, 3, 2, 2))

```

Interaction plot:

```{r}

figure3 <- f_plot_interaction_3in1(
	choice_fit = WO_top10_bottom10_choice_fit, 
	grid_std_cheating = seq(
		from = floor(min(WO_top10_bottom10_stan_data[["X_cheat_H1"]]) * 100) / 100, 
		to = ceiling(max(WO_top10_bottom10_stan_data[["X_cheat_H1"]]) * 100) / 100, 
		by = 0.01),
	mean_cheating = mean_cheating, 
	sd_cheating = sd_cheating)
figure3

```


```{r, include = FALSE}
setEPS()
postscript(here::here("figure3.eps"))
grid::grid.newpage()
grid::grid.draw(figure3)
dev.off()

png(filename = here::here("figure3.png"), 
    width = 15, height = 15, units = "cm", res = 300)
grid::grid.newpage()
grid::grid.draw(figure3)
dev.off()

```

Mean and SD cheating, by group and block:

```{r}

knitr::kable(WO_top10_bottom10_df[["use_tasks"]] %>%
		 	group_by(participant_ID,
		 		   experimental_cond,
		 		   study_half_number) %>%
		 	summarise(perc_cheat = sum(is_cheating) / n()) %>%
		 	ungroup() %>%
		 	group_by(experimental_cond,
		 		   study_half_number) %>%
		 	summarise(n(),
		 		    mean(perc_cheat),
		 		    sd(perc_cheat)),
		 digits = 2)


```

Check differences between control and stress in the percent of trials cheated during the first block.

```{r}

df_plot <- df_plot %>%
	left_join(part_info %>%
		    	select(participant_ID,
		    		 experimental_cond),
		    by = "participant_ID")

aux_check <- lm(perc_cheating ~ experimental_cond,
		    data = df_plot %>%
		    	filter(is_between_bottom_top_10perc == 1))
summary(aux_check)

```



# Results in Appendix

## All participants (n = 120)

```{r allN}

allN_df <- f_prep_use_tasks(part_info = part_info, 
				    part_and_task_info = part_and_task_info,
				    exclusion_C1 = "no_exclusion", 
				    exclusion_C2 = "no_exclusion")
allN_stan_data <- f_prep_stan_data(use_tasks = allN_df[["use_tasks"]])

allN_choice_fit <- sampling(choice_model, 
				    data = allN_stan_data,
				    chains = n_chains, 
				    iter = n_iter, 
				    seed = 25,
				    save_warmup = FALSE)
```

Check convergence (Rhat values should be 1):

```{r}
summary(summary(allN_choice_fit)[["summary"]][, "Rhat"])
```

Estimation results are:

```{r}
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = allN_choice_fit), 
		 digits = c(0, 2, 2, 3, 2, 2))
```

Mean and SD cheating, by group and block:

```{r}
knitr::kable(allN_df[["use_tasks"]] %>%
		 	group_by(participant_ID,
		 		   experimental_cond,
		 		   study_half_number) %>%
		 	summarise(perc_cheat = sum(is_cheating) / n()) %>%
		 	ungroup() %>%
		 	group_by(experimental_cond,
		 		   study_half_number) %>%
		 	summarise(n(),
		 		    mean(perc_cheat),
		 		    sd(perc_cheat)),
		 digits = 2)

```

Check differences between control and stress in the percent of trials cheated during the first block.

```{r}

aux_check <- lm(perc_cheating ~ experimental_cond,
		    data = df_plot)
summary(aux_check)

```



## Exclude top 5% and bottom 5% 

```{r WO_top5_bottom5}
WO_top5_bottom5_df <- f_prep_use_tasks(part_info = part_info, 
						   part_and_task_info = part_and_task_info,
						   exclusion_C1 = "no_exclusion", 
						   exclusion_C2 = "top_bottom_5")
WO_top5_bottom5_stan_data <- f_prep_stan_data(use_tasks = WO_top5_bottom5_df[["use_tasks"]])

WO_top5_bottom5_choice_fit <- sampling(choice_model, 
						   data = WO_top5_bottom5_stan_data,
						   chains = n_chains, 
						   iter = n_iter, 
						   seed = 25,
						   save_warmup = FALSE)
```

Check convergence (Rhat values should be 1):

```{r}
summary(summary(WO_top5_bottom5_choice_fit)[["summary"]][, "Rhat"])
```

Estimation results are:

```{r }
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_top5_bottom5_choice_fit), 
		 digits = c(0, 2, 2, 3, 2, 2))
```

Mean and SD cheating, by group and block:

```{r}
knitr::kable(WO_top5_bottom5_df[["use_tasks"]] %>%
		 	group_by(participant_ID,
		 		   experimental_cond,
		 		   study_half_number) %>%
		 	summarise(perc_cheat = sum(is_cheating) / n()) %>%
		 	ungroup() %>%
		 	group_by(experimental_cond,
		 		   study_half_number) %>%
		 	summarise(n(),
		 		    mean(perc_cheat),
		 		    sd(perc_cheat)),
		 digits = 2)

```


Check differences between control and stress in the percent of trials cheated during the first block.

```{r}

aux_df <- df_plot %>%
	inner_join(WO_top5_bottom5_df[["use_participants"]] %>%
		     	select(participant_ID),
		     by = c("participant_ID"))

aux_check <- lm(perc_cheating ~ experimental_cond,
		    data = aux_df)
summary(aux_check)

```



## Exclude top 15% and bottom 15%


```{r WO_top15_bottom15}
WO_top15_bottom15_df <- f_prep_use_tasks(part_info = part_info, 
						     part_and_task_info = part_and_task_info,
						     exclusion_C1 = "no_exclusion", 
						     exclusion_C2 = "top_bottom_15")
WO_top15_bottom15_stan_data <- f_prep_stan_data(use_tasks = WO_top15_bottom15_df[["use_tasks"]])

WO_top15_bottom15_choice_fit <- sampling(choice_model, 
						     data = WO_top15_bottom15_stan_data,
						     chains = 2, 
						     iter = 2000, 
						     seed = 25,
						     save_warmup = FALSE)
```

Check convergence (Rhat values should be 1):

```{r}
summary(summary(WO_top15_bottom15_choice_fit)[["summary"]][, "Rhat"])
```

Estimation results are:

```{r }
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_top15_bottom15_choice_fit), 
		 digits = c(0, 2, 2, 3, 2, 2))
```

Mean and SD cheating, by group and block:

```{r}
knitr::kable(WO_top15_bottom15_df[["use_tasks"]] %>%
		 	group_by(participant_ID,
		 		   experimental_cond,
		 		   study_half_number) %>%
		 	summarise(perc_cheat = sum(is_cheating) / n()) %>%
		 	ungroup() %>%
		 	group_by(experimental_cond,
		 		   study_half_number) %>%
		 	summarise(n(),
		 		    mean(perc_cheat),
		 		    sd(perc_cheat)),
		 digits = 2)

```

Check differences between control and stress in the percent of trials cheated during the first block.

```{r}

aux_df <- df_plot %>%
	inner_join(WO_top15_bottom15_df[["use_participants"]] %>%
		     	select(participant_ID),
		     by = c("participant_ID"))

aux_check <- lm(perc_cheating ~ experimental_cond,
		    data = aux_df)
summary(aux_check)

```



## Hand taken out 

```{r WO_Hand_out}
WO_Hand_out_df <- f_prep_use_tasks(part_info = part_info, 
					     part_and_task_info = part_and_task_info,
					     exclusion_C1 = "Hand_out", 
					     exclusion_C2 = "no_exclusion")
WO_Hand_out_stan_data <- f_prep_stan_data(use_tasks = WO_Hand_out_df[["use_tasks"]])

WO_Hand_out_choice_fit <- sampling(choice_model, 
					     data = WO_Hand_out_stan_data,
					     chains = n_chains, 
					     iter = n_iter, 
					     seed = 25,
					     save_warmup = FALSE)
```

Check convergence (Rhat values should be 1):

```{r}
summary(summary(WO_Hand_out_choice_fit)[["summary"]][, "Rhat"])
```

Estimation results are:

```{r }
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_Hand_out_choice_fit), 
		 digits = c(0, 2, 2, 3, 2, 2))
```

Mean and SD cheating, by group and block:

```{r}
knitr::kable(WO_Hand_out_df[["use_tasks"]] %>%
		 	group_by(participant_ID,
		 		   experimental_cond,
		 		   study_half_number) %>%
		 	summarise(perc_cheat = sum(is_cheating) / n()) %>%
		 	ungroup() %>%
		 	group_by(experimental_cond,
		 		   study_half_number) %>%
		 	summarise(n(),
		 		    mean(perc_cheat),
		 		    sd(perc_cheat)),
		 digits = 2)

```

Check differences between control and stress in the percent of trials cheated during the first block.

```{r}

aux_df <- df_plot %>%
	inner_join(WO_Hand_out_df[["use_participants"]] %>%
		     	select(participant_ID),
		     by = c("participant_ID"))

aux_check <- lm(perc_cheating ~ experimental_cond,
		    data = aux_df)
summary(aux_check)

```


```{r }

plot_allN <- f_plot_interaction_single(
	choice_fit = allN_choice_fit, 
	grid_std_cheating = seq(
		from = floor(min(allN_stan_data[["X_cheat_H1"]]) * 100) / 100, 
		to = ceiling(max(allN_stan_data[["X_cheat_H1"]]) * 100) / 100,
		by = 0.01),
	mean_cheating = mean_cheating,
	sd_cheating = sd_cheating)

plot_WO_top5_bottom5 <- f_plot_interaction_single(
	choice_fit = WO_top5_bottom5_choice_fit, 
	grid_std_cheating = seq(
		from = floor(min(WO_top5_bottom5_stan_data[["X_cheat_H1"]]) * 100) / 100, 
		to = ceiling(max(WO_top5_bottom5_stan_data[["X_cheat_H1"]]) * 100) / 100,
		by = 0.01),
	mean_cheating = mean_cheating,
	sd_cheating = sd_cheating)

plot_WO_top15_bottom15 <- f_plot_interaction_single(
	choice_fit = WO_top15_bottom15_choice_fit, 
	grid_std_cheating = seq(
		from = floor(min(WO_top15_bottom15_stan_data[["X_cheat_H1"]]) * 100) / 100, 
		to = ceiling(max(WO_top15_bottom15_stan_data[["X_cheat_H1"]]) * 100) / 100,
		by = 0.01),
	mean_cheating = mean_cheating,
	sd_cheating = sd_cheating)

plot_WO_hand_out <- f_plot_interaction_single(
	choice_fit = WO_Hand_out_choice_fit, 
	grid_std_cheating = seq(
		from = floor(min(WO_Hand_out_stan_data[["X_cheat_H1"]]) * 100) / 100, 
		to = ceiling(max(WO_Hand_out_stan_data[["X_cheat_H1"]]) * 100) / 100,
		by = 0.01),
	mean_cheating = mean_cheating,
	sd_cheating = sd_cheating)

plot_allN <- plot_allN + 
	labs(title = paste0("a) n = ", nrow(allN_df[["use_participants"]]),
				  "\n(full sample)"))
plot_WO_top5_bottom5 <- plot_WO_top5_bottom5 + 
	labs(title = paste0("b) n = ", nrow(WO_top5_bottom5_df[["use_participants"]]),
				  " (excl. top and \n bottom 5%)"))
plot_WO_top15_bottom15 <- plot_WO_top15_bottom15 + 
	labs(title = paste0("c) n = ", nrow(WO_top15_bottom15_df[["use_participants"]]),
				  " (excl. top and \n bottom 15%)"))
plot_WO_hand_out <- plot_WO_hand_out + 
	labs(title = paste0("d) n = ", nrow(WO_Hand_out_df[["use_participants"]]),
				  " (excl. n = 6 \n who withdrew their hand)"))

SM_plot <- ggpubr::ggarrange(plot_allN, 
				     plot_WO_top5_bottom5,
				     plot_WO_top15_bottom15, 
				     plot_WO_hand_out,
				     nrow = 2,
				     ncol = 2,
				     common.legend = TRUE,
				     legend = "bottom")
SM_plot

```


```{r, include = FALSE}
setEPS()
postscript(here::here("figureSM.eps"))
SM_plot
dev.off()

png(filename = here::here("figureSM.png"), 
    width = 15, height = 15, units = "cm", res = 300)
SM_plot
dev.off()

```


# Info about R packages

```{r}
sessionInfo()
```




