---
title: "Analysis for the Stress and Honesty project"
author: "Ana Martinovici"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_float: 
            collapsed: false
        number_sections: true
        code_folding: hide
        theme: cerulean
editor_options: 
  chunk_output_type: console
---

This file includes the analysis for "The effect of acute stress on dishonesty: the moderating role of moral default" (Sebastian P.H. Speer, Ana Martinovici, Ale Smidts, Maarten A.S. Boksem).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages-and-data}

library("tidyverse")
library("rstan")
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())	

load(here::here("data.RData"))
source(here::here("f_aux_functions.R"))
choice_model <- stan_model(here::here("LOGIT.stan"))
choice_pars <- c("gamma_00", "gamma_std_cheat", "gamma_stress", "gamma_std_cheat_stress")

```

# Data summaries

We have `r nrow(part_info)` participants. 

Gender split: `r knitr::kable(part_info %>% group_by(Gender) %>% summarise(n = n()))` 

Age (values rounded to 2 decimals): 
mean = `r round(mean(part_info[["Age"]]), 2)` and 
SD = `r round(sd(part_info[["Age"]]), 2)`.

Each participant completes the same number of tasks, see that the min and max number of tasks per participant are equal:

```{r data-part1}
knitr::kable(part_and_task_info %>%
		 	group_by(participant_ID) %>%
		 	summarise(n_tasks_per_i = n()) %>%
		 	summarise(min_n_tasks = min(n_tasks_per_i),
		 		    max_n_tasks = max(n_tasks_per_i)))
```

Not all tasks provide an opportunity to cheat. For some tasks, participants had to use a mouse to indicate the differences between pictures, so there was no opportunity to say "Yes, I found all 3 differences" without showing them. 
All participants complete the same number of **click tasks**, see that the min and max number of click tasks are equal:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "click") %>%
		 	group_by(participant_ID) %>%
		 	summarise(n_tasks_per_i = n()) %>%
		 	summarise(min_n_tasks = min(n_tasks_per_i),
		 		    max_n_tasks = max(n_tasks_per_i)))

```

For no-click tasks, the split between trials with 1, 2, or 3 differences is:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "noclick") %>% 
		 	group_by(n_differences) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	mutate(perc_tasks = n_tasks / sum(n_tasks)),
		 digits = 2)

```

For no-click tasks, the split by reward:

```{r}
knitr::kable(part_and_task_info %>% 
		 	filter(type_of_task == "noclick") %>% 
		 	group_by(reward) %>%
		 	summarise(n_tasks = n()) %>%
		 	ungroup() %>%
		 	mutate(perc_tasks = n_tasks / sum(n_tasks)),
		 digits = 2)

```

# Results

## Plot % cheating in first half

```{r}
df_plot <- part_and_task_info %>%
	filter(type_of_task == "noclick") %>%
	filter(n_differences %in% c(1, 2)) %>%
	filter(reward %in% c(0.20, 0.40)) %>%
	filter(part_response %in% c("No, did not find 3 diffs", "Yes, found 3 diffs")) %>%
	filter(is_in_second_half == 0)

df_plot <- df_plot %>%
	group_by(participant_ID) %>%
	summarise(perc_cheating = sum(part_response == "Yes, found 3 diffs") / n()) %>%
	ungroup()

mean_cheating <- mean(df_plot$perc_cheating)
sd_cheating   <- sd(df_plot$perc_cheating)

df_plot <- df_plot %>%
	mutate(std_perc_cheating = (perc_cheating - mean_cheating) / sd_cheating)

bottom_10perc <- quantile(df_plot$std_perc_cheating, probs = c(0.10))
top_10perc    <- quantile(df_plot$std_perc_cheating, probs = c(0.90))

df_plot <- df_plot %>%
	mutate(is_between_bottom_top_10perc = 
		 	(std_perc_cheating >= bottom_10perc)*
		 	(std_perc_cheating <= top_10perc))

df_plot <- df_plot %>%
	arrange(perc_cheating) %>%
	mutate(cheat_number = row_number()) %>%
	mutate(f_fill = factor(is_between_bottom_top_10perc,
				     levels = c(0, 1),
				     labels = c("bottom", "middle")))

df_plot %>% 
	ggplot(aes(x = cheat_number, y = perc_cheating)) +
	geom_col(aes(fill = f_fill), width = 0.9, alpha = 0.50) +
	theme_bw() +
	ylab("Percent cheating at t = 1") +
	xlab("Participant") +
	scale_x_continuous(breaks = c(1, 60, 120)) + 
	scale_fill_manual("", 
				breaks = c("bottom", "middle"),
				values = c("middle" = "blue", # "#00A9FF"
					     "bottom" = "grey50"),
				labels = c("bottom" = "Bottom 10% and top 10%",
					     "middle" = "Analysis sample (n = 97)")) +
	guides(fill = guide_legend(nrow = 2)) +
	theme(legend.position = "bottom") 

```

The average percent cheating for the bottom 10% and top 10% is:

```{r}

df_plot %>%
	filter(is_between_bottom_top_10perc == 0) %>%
	mutate(group_name = if_else(std_perc_cheating < 0, "bottom_10", "top_10")) %>%
	group_by(group_name) %>%
	summarise(n_obs = n(),
		    mean_perc_cheating = mean(perc_cheating)) 

```



## Model estimation results (n = 97)

```{r WO_top10_bottom10}
WO_top10_bottom10_stan_data <- f_prep_stan_data(part_info = part_info, 
								part_and_task_info = part_and_task_info,
								exclusion_C1 = "no_exclusion", 
								exclusion_C2 = "top_bottom_10")
WO_top10_bottom10_choice_fit <- sampling(choice_model, 
						     data = WO_top10_bottom10_stan_data,
						     chains = 2, 
						     iter = 2000, 
						     seed = 25,
						     save_warmup = FALSE)
```

`Rhat` values for this model:

```{r}
summary(summary(WO_top10_bottom10_choice_fit)[["summary"]][, "Rhat"])
```

There are n = `r length(WO_top10_bottom10_stan_data[["X_in_stress_group"]])` participants, split between the control (n = `r length(WO_top10_bottom10_stan_data[["X_in_stress_group"]]) - sum((WO_top10_bottom10_stan_data[["X_in_stress_group"]]))`) and the stress (n = `r sum((WO_top10_bottom10_stan_data[["X_in_stress_group"]]))`) groups.

Estimation results are:

```{r}
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_top10_bottom10_choice_fit), 
		 digits = 2)
```

Interaction plot:

```{r}
f_plot_interaction(choice_fit = WO_top10_bottom10_choice_fit, 
			 choice_pars = choice_pars, 
			 grid_std_cheating = seq(
			 	from = floor(min(WO_top10_bottom10_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	to = ceiling(max(WO_top10_bottom10_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	by = 0.01))

```


# Results in Appendix

## All participants (n = 120)

```{r allN}
allN_stan_data <- f_prep_stan_data(part_info = part_info, 
					     part_and_task_info = part_and_task_info,
					     exclusion_C1 = "no_exclusion", 
					     exclusion_C2 = "no_exclusion")
allN_choice_fit <- sampling(choice_model, 
				    data = allN_stan_data,
				    chains = 2, 
				    iter = 2000, 
				    seed = 25,
				    save_warmup = FALSE)
```

`Rhat` values for this model:

```{r}
summary(summary(allN_choice_fit)[["summary"]][, "Rhat"])
```

There are n = `r length(allN_stan_data[["X_in_stress_group"]])` participants, split between the control (n = `r length(allN_stan_data[["X_in_stress_group"]]) - sum((allN_stan_data[["X_in_stress_group"]]))`) and the stress (n = `r sum((allN_stan_data[["X_in_stress_group"]]))`) groups.

Estimation results are:

```{r}
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = allN_choice_fit), 
		 digits = 2)
```

Interaction plot:

```{r }
f_plot_interaction(choice_fit = allN_choice_fit, 
			 choice_pars = choice_pars, 
			 grid_std_cheating = seq(
			 	from = floor(min(allN_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	to = ceiling(max(allN_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	by = 0.01))

```


## Exclude top 5% and bottom 5% (n = 108) 

```{r WO_top5_bottom5}
WO_top5_bottom5_stan_data <- f_prep_stan_data(part_info = part_info, 
							    part_and_task_info = part_and_task_info,
							    exclusion_C1 = "no_exclusion", 
							    exclusion_C2 = "top_bottom_5")

WO_top5_bottom5_choice_fit <- sampling(choice_model, 
						   data = WO_top5_bottom5_stan_data,
						   chains = 2, 
						   iter = 2000, 
						   seed = 25,
						   save_warmup = FALSE)
```

`Rhat` values for this model:

```{r}
summary(summary(WO_top5_bottom5_choice_fit)[["summary"]][, "Rhat"])
```

There are n = `r length(WO_top5_bottom5_stan_data[["X_in_stress_group"]])` participants, split between the control (n = `r length(WO_top5_bottom5_stan_data[["X_in_stress_group"]]) - sum((WO_top5_bottom5_stan_data[["X_in_stress_group"]]))`) and the stress (n = `r sum((WO_top5_bottom5_stan_data[["X_in_stress_group"]]))`) groups.

Estimation results are:

```{r }
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_top5_bottom5_choice_fit), 
		 digits = 2)
```

Interaction plot:

```{r }
f_plot_interaction(choice_fit = WO_top5_bottom5_choice_fit, 
			 choice_pars = choice_pars, 
			 grid_std_cheating = seq(
			 	from = floor(min(WO_top5_bottom5_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	to = ceiling(max(WO_top5_bottom5_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	by = 0.01))

```


## Exclude top 15% and bottom 15% (n = 86)


```{r WO_top15_bottom15}
WO_top15_bottom15_stan_data <- f_prep_stan_data(part_info = part_info, 
								part_and_task_info = part_and_task_info,
								exclusion_C1 = "no_exclusion", 
								exclusion_C2 = "top_bottom_15")

WO_top15_bottom15_choice_fit <- sampling(choice_model, 
						     data = WO_top15_bottom15_stan_data,
						     chains = 2, 
						     iter = 2000, 
						     seed = 25,
						     save_warmup = FALSE)
```

`Rhat` values for this model:

```{r}
summary(summary(WO_top15_bottom15_choice_fit)[["summary"]][, "Rhat"])
```

There are n = `r length(WO_top15_bottom15_stan_data[["X_in_stress_group"]])` participants, split between the control (n = `r length(WO_top15_bottom15_stan_data[["X_in_stress_group"]]) - sum((WO_top15_bottom15_stan_data[["X_in_stress_group"]]))`) and the stress (n = `r sum((WO_top15_bottom15_stan_data[["X_in_stress_group"]]))`) groups.

Estimation results are:

```{r }
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_top15_bottom15_choice_fit), 
		 digits = 2)
```

Interaction plot:

```{r }
f_plot_interaction(choice_fit = WO_top15_bottom15_choice_fit, 
			 choice_pars = choice_pars, 
			 grid_std_cheating = seq(
			 	from = floor(min(WO_top15_bottom15_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	to = ceiling(max(WO_top15_bottom15_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	by = 0.01))

```

## Hand taken out (n = 114)

```{r WO_Hand_out}
WO_Hand_out_stan_data <- f_prep_stan_data(part_info = part_info, 
							part_and_task_info = part_and_task_info,
							exclusion_C1 = "Hand_out", 
							exclusion_C2 = "no_exclusion")

WO_Hand_out_choice_fit <- sampling(choice_model, 
					     data = WO_Hand_out_stan_data,
					     chains = 2, 
					     iter = 2000, 
					     seed = 25,
					     save_warmup = FALSE)
```

`Rhat` values for this model:

```{r}
summary(summary(WO_Hand_out_choice_fit)[["summary"]][, "Rhat"])
```

There are n = `r length(WO_Hand_out_stan_data[["X_in_stress_group"]])` participants, split between the control (n = `r length(WO_Hand_out_stan_data[["X_in_stress_group"]]) - sum((WO_Hand_out_stan_data[["X_in_stress_group"]]))`) and the stress (n = `r sum((WO_Hand_out_stan_data[["X_in_stress_group"]]))`) groups.

Estimation results are:

```{r }
knitr::kable(f_sum_results(par_names = choice_pars, 
				   stan_fit = WO_Hand_out_choice_fit), 
		 digits = 2)
```

Interaction plot:

```{r }
f_plot_interaction(choice_fit = WO_Hand_out_choice_fit, 
			 choice_pars = choice_pars, 
			 grid_std_cheating = seq(
			 	from = floor(min(WO_Hand_out_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	to = ceiling(max(WO_Hand_out_stan_data[["X_cheat_H1"]]) * 100) / 100, 
			 	by = 0.01))

```

# Info about R packages

```{r}
sessionInfo()
```


